\documentclass[letterpaper,10pt]{article}

\usepackage{geometry}
\usepackage{hyperref}
\geometry{textheight=8.5in, textwidth=6in}

\newcommand{\toc}{\tableofcontents}

\def\name{Helena A. Bales}
\title{CS 444 Project 4: The SLOB SLAB}
\author{Helena A. Bales, Kathryn Maule, and Alexander Scott Wilson }

\parindent = 0.0 in
\parskip = 0.1 in

\begin{document}
\maketitle

\begin{abstract}
   For the SLOB SLAB assignment we will be implementing code in the default yocto kernel. 
   The purpose of this assignment is to understnad how the SLOB first-fit algorithm works, through 
   the implementation of the afforementioned algorithm. We will also be implementing the best-fit 
   allocation algorithm. We will be writing a program that computes the efficiency of both 
   algorithms and compare the fragmentation suffered by each. The solution to this problem will be 
   implemented within the default yocto kernel.
\end{abstract}

\clearpage

\tableofcontents

\clearpage

\section{Program Design}
\subsection{Description of Problem}
The SLOB SLAB assignment will require the implementation of code in the default Linux yocto kernel. 
The algorithms that will be implemented are the SLOB first-fit algorithm and the best-fit allocation
 algorithm. In addition to these two algorithms, we will be measuring the efficiency of both 
 algorithms, and we will compare the fragmentation suffered by each. Measuring the efficiency will 
 require the addition of a system call that will measure the actual memory usage. This program will 
 be developed in the slob.c file in the mm directory of the Linux kernel.

 There are additional hints given by the assignment description that may be useful for the design of
 the implementation of these algorithms. These hints include that the best-fit must be over all 
allocated pages, not just the current page. Additionally, we must pick a system call number that 
has never been used for measuring the actual memory usage. Finally we will also need to be careful
 with our memory tracking, and that SLOB is just a simple list of blocks. With the help of these 
hints we should be able to complete the tasks described above as well as the following sections 
of documentation.

\subsection{Design of SLOB First-Fit Algorithm}
\subsection{Design of Best-Fit Allocation Algorithm}
\subsection{Design of Effeciency and Fragmentation Measurement Script}
The script that measures the effeciency of the algorithms will run each algorithm for a series of 
different inputs. The script will allocate various sizes of memory using each method. The 
measurement of the efficiency will be accomplished by measuring the total time required to allocate 
all memory blocks using each method. The times will be output to a CSV along with the number of 
blocks allocated during the test.

The script which measures the fragmentation of each implementation of the algorithm will be 
performed on the output of the effeciency test. After the allocation of each memory block has 
occured, a check will be run on the used memory for each algorithm. This will be accomplished using 
a system call. The fragementation suffered by the memory blocks allocated by each algorithm will be 
output to the same CSV as the effeciency measurements.

\section{Version Control Logs}
\input{changelog.tex}

\section{Work Log}
\subsection{November 22nd, 2016 - 11:00 am}
Added Makefile, changes script, and tex document. 
The changes script generates a change log tex document to be included in the tex write up that formats 
the commit log as a table. 
The tex document (this document) contains all documentation on the project. 
The Makefile will compile this document and the table of commits into a pdf.

\subsection{November 28nd, 2016 - 2:30 pm}
Wrote assignment abstract and started Program Design.
Added subsection for the description of the problem, which includes an overview of the project 
description given on the CS444 class website.
Added content in sections for purpose of assignment, testing methods, and learning outcomes.

\subsection{November 28nd, 2016 - 3:00 pm}
Wrote content for design of efficiency and fragmentation measurement algorithms.

\section{Purpose of Assignment}
The purpose of this assignment is to understand how the SLOB first-fit algorithm and the best-fit 
allocation algorithm work through the implementation of each algorithm, the measuring of their 
efficiencies, and comparing the fragmentation caused by each algorithm. This will help us understand
 the way that the allocation of memory blocks works in Linux systems. The algorithms and algorithm 
analytics will be implemented in the default Linux yocto kernel, which should help us understand the
 portion of the implementation that is Linux-specific.

\section{Testing Methods}
We will be testing the implementations of these algorithms through measuring their efficiency and 
comparing the fragmentation caused by each of the algorithms. We will measure the efficiency by 
writing a test script that will run the algorithms with a variety of inputs and measure the runtime 
of each trial. From there we should be able to equate the runtimes with a complexity using the data.
 Measuring the fragmentation of each algorithms will require adding a system call which will return 
 the memory usage. This test script should store the results in a CSV which can then be used as the 
 input to create any desired graph.

\section{Learning Outcomes}
From this assignment we will learn how to implement SLOB first-fit algorithm and a best-fit 
allocation algorithm. We will learn how to make a system call to measure the fragmentation caused by each of the algorithms. We will learn how to measure and calculate the efficiency of the 
algorithms. We learned how to do all this within the Linux yocto kernel.

\end{document}
